Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2015-03-30 tese/template_project_latex.tex
[ADD] added more bullets
[ADD] added stroph.js (maybe it will be a reference)
[ADD] added text about SIP and XMPP

@@

  \subsubsection{Local Storage}
  \subsubsection{Video Recording}
  \subsubsection{Video Playback - Past and Present}

>>>>

Compared to Skype, WebRTC allows web browser real time communications without installing any aditional application or plugin.

\section{\color{red}Signaling}

  WebRTC doesn't implement signaling, different applications may need different protocols, there is no single answer that fits all problems. Amongst multiple options, signaling can be done by using SIP, XMPP, WebSockets, Socket.io or by implementing a custom protocol.

  %https://bloggeek.me/siganling-protocol-webrtc/
  {\color{red}[SIP]}

  SIP is a signaling method, it allows web browsers to have audio, video and SMS capabilities like mobile phones. For instance, it's possible to interoperate with SIP, mobile and fixed phones.

  SIP is used in VoIP applications duo its compatibility with PSTN. Service providers are disponibilizing access to their SIP infrastrucures through WebSockets. Frameworks like JSSip or sipML5 are used on client side to encode SIP messages, making SIP accessible to web based applications.

  {\color{red}[XMPP]}

  HTTP works on a request followed by a server response. Sometimes it's required that some informations are obtained in real time, as we saw, some NAT's don't suport callbacks from servers, one technique to overcome this problem is polling.

  Polling consists on sending periodic messages that the server responds imediately with empty content or fresh information. Simple polling wastes network bandwith and energy. Long polling consists on making the server wait until there is fresh information or expiring after some time. Long polling returns answers faster than simple polling.

  XMPP's bi-directional communication is achieved through BOSH, which basically consists on long polling.

@@

  {\color{red}[Local Storage]}

  {\color{red}[Video Recording]}

  {\color{red}[Video Playback - Past and Present]}
